Revisiting the Relationship between Short-Chain Fatty Acids, the Microbiota, and Colorectal Tumors

### 2018-08-07 submission/manuscript.Rmd
P3 ada suggestions

One possible technical limitation is that a fecal sample may not be an ideal type of bio-specimen and that the effect SCFAs have on tumorigenesis is only detected in the colon. However, this is unlikely to be a major confounder. First, most *in vivo* studies as well as human studies have used fecal material in their analysis [@Ohigashi2013; @Bishehsari2018]. Second, previous studies that measure SCFA changes after fiber supplementation use fecal material to track these responses with a great deal of success [@scfa_measures_venkataraman2016]. Although there are limitations with the current research on SCFAs and colorectal tumors, technical limitations are less likely to be cause of this. Additionally, as mentioned earlier, our observations along with the randomized controlled trials on fiber supplementation in tumor recurrence [@Yao2017] provide evidence that these specific metabolites may not be protective or used as a general treatment option in colorectal cancer. Yet, taxa that are associated with SCFA production are consistently higher in individuals without colon tumors than patients with carcinomas [@Shah2017; @normalization_Sze2017; @meta_analysis_crc_Sze2018].

>>>>

One possible technical limitation is that a fecal sample may not be an ideal type of bio-specimen and that the effect SCFAs have on tumorigenesis is only detected in the colon. However, this is unlikely to be a major confounder. First, most *in vivo* studies, as well as human studies, have used fecal material in their analysis [@Ohigashi2013; @Bishehsari2018]. Second, previous studies that measure SCFA changes after fiber supplementation use fecal material to track these responses with a great deal of success [@scfa_measures_venkataraman2016]. Although there are limitations with the current research on SCFAs and colorectal tumors, technical limitations are less likely to be the cause of this. Clearly, our observations provide robust evidence that these specific metabolites may not be protective or used as a general treatment option in colorectal cancer. Yet, taxa that are associated with SCFA production are consistently higher in individuals without colon tumors than patients with carcinomas [@Shah2017; @normalization_Sze2017; @meta_analysis_crc_Sze2018].

### 2018-08-07 submission/manuscript.tex
P3 ada suggestions

One possible technical limitation is that a fecal sample may not be an
ideal type of bio-specimen and that the effect SCFAs have on
tumorigenesis is only detected in the colon. However, this is unlikely
to be a major confounder. First, most \emph{in vivo} studies as well as
human studies have used fecal material in their analysis (18, 19).
Second, previous studies that measure SCFA changes after fiber
supplementation use fecal material to track these responses with a great
deal of success (24). Although there are limitations with the current
research on SCFAs and colorectal tumors, technical limitations are less
likely to be cause of this. Additionally, as mentioned earlier, our
observations along with the randomized controlled trials on fiber
supplementation in tumor recurrence (20) provide evidence that these
specific metabolites may not be protective or used as a general
treatment option in colorectal cancer. Yet, taxa that are associated
with SCFA production are consistently higher in individuals without
colon tumors than patients with carcinomas (10, 11, 27).

>>>>

One possible technical limitation is that a fecal sample may not be an
ideal type of bio-specimen and that the effect SCFAs have on
tumorigenesis is only detected in the colon. However, this is unlikely
to be a major confounder. First, most \emph{in vivo} studies, as well as
human studies, have used fecal material in their analysis (18, 19).
Second, previous studies that measure SCFA changes after fiber
supplementation use fecal material to track these responses with a great
deal of success (24). Although there are limitations with the current
research on SCFAs and colorectal tumors, technical limitations are less
likely to be the cause of this. Clearly, our observations provide robust
evidence that these specific metabolites may not be protective or used
as a general treatment option in colorectal cancer. Yet, taxa that are
associated with SCFA production are consistently higher in individuals
without colon tumors than patients with carcinomas (10, 11, 27).
